\documentclass{book}
\usepackage[letterpaper,inner=46,top=48,bottom=48,outer=46]{geometry}
\usepackage{multicol,textcomp}
\usepackage{fontspec}
\setmainfont{Souvenir Demi}

\begin{document}

\title{Dungeons \& Dragons\textsuperscript{\textregistered} Players Manual}
\maketitle

\pagebreak
\huge{Preface}
\scriptsize
\begin{multicols}{3}
\noindent{This is a game that is fun. It helps you imagine.}\\
\\
\noindent{\textit{"As you whirl around, your sword ready, the huge, red, fire-breathing dragon swoops toward you with a ROAR!"}}\\
\\
\noindent{See? Your imagination woke up already. Now imagine: This game may be more fun than any other game you have ever played!}\\
\indent{The DUNGEONS \& DRAGONS\textsuperscript{\textregistered}\ game is a way for us to imagine together -- like watching the same movie, or reading the same book. But you can write the stories, without putting a word on paper -- just by playing the D\&D\textsuperscript{\textregistered}\ game.}\\
\indent{You, along with your friends, will create a great fantasy story, you will put it away after each game, and go back to school or work, but -- like a book -- the adventure will wait. It?s better than a book, though; it will keep going as long as you like.}\\
\indent{It is nearly the most popular game\columnbreak\ ever made. And you will see why, in just a bit.}\\
\indent{When you bought some other game or book, did you ever think, ?Gee, that?s nice, but it?s not quite what I thought it would be?? Well, your D\&D adventures will be just what you want, because you?re the one making them up!}\\
\indent{And it?s not hard. It takes a little reading and a little thinking, but most of all, it?s fun.}\\
\indent{It?s fun when you discover that nobody loses, and everybody wins!}\\
\indent{It?s fun when you get good at the game . . . for example, knowing what to expect in a kobold cave, and which dragons are on your side.}\\
\indent{And you don?t have to put in a coin each time, like many other games. Once you have these rules, you don?t need anything else.}\\
\\
\indent{There?s more, of course, if you want it: exciting adventures to play, miniature figures of monsters and characters, expert rules for more experienced players, and\columnbreak\ lots more. But you already have everything you need to start: this package, and your imagination. That will do it.}\\
\indent{Ah, yes; it does cost one more thing, which you also have right now -- a bit of time. It takes a few minutes to learn the basic rules, and another hour or two to play a full game. You will probably want to spend more time, and might even make it a hobby; millions of people have.}\\
\indent{But for now, just sit back and imagine.}\\

\noindent{\textit{"Your character stands atop a grassy hill . . . the sun glints off your golden hair, rippling in the warm breeze . . . you absent-mindedly rub the gem-studded hilt of your magic sword, and glance over at the dwarf and elf, bickering as sual about how to load the horses . . . the magic-user has memorized her spells, and says he?s ready to go . . . a dangerous dungeon entrance gapes at you from the mountain nearby, and inside, a fearsome dragon awaits. Time to get moving. . ."}}\\
\noindent{Have Fun!}\\
\begin{flushright}
Frank Mentzer\\
February, 1983\\
\end{flushright}

\end{multicols}
\end{document}
